Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
Fix things

\libmotmot implements a slightly simplified variant of the Multi-Paxos
algorithm, augmented by a number of out-of-band yet nonetheless indispensible
side protocols.  This core Paxos implementation is wrapped by a client
interface and uses MessagePack \cite{msgpack} for network communication.
As with the other components of \Motmot, \libmotmot makes use of the GNOME
Library (GLib) \cite{glib}.

@@

We found that these two libraries provided good abstractions for the task of
implementing a server. Gevent's coroutines provided an extremely useful
concurrency model: they were executed in a single thread, so synchronization
around global objects was not necessary, while avoiding the complexity (and
unnecessary indentation) of a callback-based system. Msgpack also provided an
excellent abstraction, allowing the server to assume that arbitrary data
structures could be written to and read from the wire. The ad-hoc nature of the
format also helped speed development of the server and protocol.

% TODO: cite pyopenssl
Finally, we used openssl (and the pyOpenSSL library in particular) to perform
certificate operations.

>>>>

\libmotmot implements a slightly simplified variant of the Multi-Paxos
algorithm, augmented by a number of out-of-band yet nonetheless indispensable
side protocols.  This core Paxos implementation is wrapped by a client
interface and uses MessagePack \cite{msgpack} for network communication.
As with the other components of \Motmot, \libmotmot makes use of the GNOME
Library (GLib) \cite{glib}.

@@

We found that these two libraries provided good abstractions for the task of
implementing a server. Gevent's coroutines provided an extremely useful
concurrency model: they were executed in a single thread, so synchronization
around global objects was not necessary, while avoiding the complexity (and
unnecessary indentation) of a callback-based system. MessagePack also provided an
excellent abstraction, allowing the server to assume that arbitrary data
structures could be written to and read from the wire. The ad-hoc nature of the
format also helped speed development of the server and protocol.

% TODO: cite pyopenssl
Finally, we used \texttt{openssl} (and the \texttt{pyOpenSSL} library in
particular) to perform certificate operations.
